---
title: "Lab 01 - Hello R"
author: "keyu wu"
date: "02/06/2021"
output: github_document
---
## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

1846 rows and 3 variables.

### Exercise 2

Plot y vs. x for the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino, fig.height=3, fig.width=6 }
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plot y vs. x for the star dataset:

```{r plot-star, fig.height=3, fig.width=3}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

calculate the correlation between `x` and `y` in this dataset:

```{r cor-star, fig.height=3, fig.width=3}
star_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4

Plot y vs. x for the circle dataset:

```{r plot-circle, fig.height= 3, fig.width=4}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y))+ geom_point()
```

calculate the correlation between `x` and `y` in this dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor (x,y))

```

### Exercise 5

plot all datasets:

```{r plot-all, fig.height=7, fig.width=5}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+geom_point()+
  facet_wrap(~ dataset, ncol = 3)+
  theme (legend.position = "none")
```

generate all the summary correlation coefficients:

```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset)%>%
  summarize ( r = cor (x,y)) %>%
  print(13)

```

